---
title: "Journal (reproducible report)"
author: "Nana Sekyere Lewis"
date: "2020-11-05"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# My first post
```{r}
# Data Science at TUHH ------------------------------------------------------


#Challenge 1 -Introduction to the Tidyverse ----


# 1.0 Load libraries ----

library(tidyverse)
library(readxl)


# 2.0 Importing Files ----

# A good convention is to use the file name and suffix it with tbl for the data structure tibble
bikes_tbl      <- read_excel(path = "~/R_scripts/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("~/R_scripts/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

# Not necessary for this analysis, but for the sake of completeness
bikeshops_tbl  <- read_excel("~/R_scripts/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")


# 3.0 Examining Data ----

left_join(orderlines_tbl, bikes_tbl, by = c("product.id" = "bike.id"))

# 4.0 Joining Data ----

# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))


# 5.0 Wrangling Data ----

bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 4.1 Separate category name
  separate(col    = category,
           into   = c("category.1", "category.2", "category.3"),
           sep    = " - ") %>%
  
  # 4.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  
  # 4.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 4.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 4.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  
  # 4.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>% 
  
  # 4.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 4.4 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))

#Check location multiple features (State and city)
#bike_orderlines_wrangled_tbl$location

#Probably unecessary code but also helps to see just the location column
bike_orderlines_wrangled_tbl %>% 
  select(location) %>%
  filter(str_detect(location, "^Hamburg"))

#Challenge begins
#4.5 Split location into state and city
bike_orderlines_wrangled2_tbl <- bike_orderlines_wrangled_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = (",")) 


# 6.0 Business Insights ----
# 6.1 Sales by location (State) ----


# Step 1 - Manipulate

sales_by_state_tbl <- bike_orderlines_wrangled2_tbl %>%
  # Select columns
  select(state, total_price) %>%
  
  # Grouping by state and summarizing sales
  group_by(state) %>% 
  summarize(sales = sum(total_price)) %>%
  
  # Add a column that turns the numbers into a currency format 
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

sales_by_state_tbl

# Step 2 - Visualize

#Plot bar chart(This is for Rmarkdown. Not sure how to use that just about yet)
#```{r plot, fig.width=10, fig.height=7}

#step 2: Visualize
#plot a bar chart
sales_by_state_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  #geom_label(aes(label = sales_text)) + # Adding labels to the bars
  #geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by state",
    #subtitle = "Upward Trend",
    x = "state", # Override defaults for x and y
    y = "Revenue")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))#rotate x-axis 


# 6.2 Sales by Location (State) and Category 2 ----
library(lubridate)

# Step 1 - Manipulate

sales_by_year_by_state_tbl <- bike_orderlines_wrangled2_tbl %>%
  
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%
  
  # Group by and summarize year and state
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%
  
  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €")) %>%
  arrange(desc(sales))

sales_by_year_by_state_tbl


# Step 2 - Visualize

#Plot bar chart(facet_wrap)
sales_by_year_by_state_tbl %>%
  
  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +
  
  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  
  # Facet
  facet_wrap(~ state) +
  
  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and state",
    fill = "State" # Changes the legend name
  )+ 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


# 7.0 Writing Files ----

#6.1 Excel ----
library("writexl")
bike_orderlines_wrangled2_tbl %>%
  write_xlsx("~/R_scripts/DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines2.xlsx")

# 6.2 CSV ----
bike_orderlines_wrangled2_tbl %>% 
  write_csv("~/R_scripts/DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines2.csv")

# 6.3 RDS ----
bike_orderlines_wrangled2_tbl %>% 
  write_rds("~/R_scripts/DS_101/00_data/01_bike_sales/02_wrangled_data/bike_orderlines2.rds")
```





Last compiled: `r Sys.Date()`

Notice that whatever you define as a top level header, automatically gets put into the table of contents bar on the left. 

## Second level header

You can add more headers by adding more hashtags. These won't be put into the table of contents

### third level header

Here's an even lower level header

# My second post (note the order)

```{r}


#Challenge 2.0 : Data Acquisition ----
#Load Relevant Packages


library(glue)
library(httr)
library(purrr)
library(tidyverse) 
library(rvest)     
library(xopen)     
library(jsonlite)  
library(stringi)  
library(jsonlite)



#2.1: Data from an API ----
#A COVID API.

coro_url <- "https://api.covid19api.com/"


xopen(coro_url) # Open links directly from RStudio to inspect them


#lets try to get something
coro_data <- GET(coro_url)
coro_data


coro_data_list <- coro_data %>%
  .$content %>%
  rawToChar() %>%
  fromJSON()
coro_data_list



#2.2: Web Scraping ----

#Task: Scrape one of the competitor websites of canyon
#(either https://www.rosebikes.de/ or https://www.radon-bikes.de) 
#create a small database.
#database should contain the "model names" and "prices" for 
#"at least one category". 
#Print the first 10 rows of your tibbles. 


#2.2.1 Bicycle Categories ----

#assign the  URL to a variable
rosebikes_category_url <- "https://www.rosebikes.de/fahrr%C3%A4der"
xopen(rosebikes_category_url)



#read in the html from the URL
rosebikes_category_html <- rosebikes_category_url %>%
  read_html() 

# Select the correct html nodes and extract the category
rosebikes_categories_tbl <-rosebikes_category_html %>%
  html_nodes(css =".catalog-navigation__list-item > a ") %>%
  html_attr("title") %>%
  
  #turn the vector into a table
  enframe(name = "position", value = "category")
rosebikes_categories_tbl



#2.2.2 Model and Price ----

#now to get the models under "kinder"
rosebikes_kinder_url <- "https://www.rosebikes.de/fahrr%C3%A4der/kinder"
#xopen(rosebikes_kinder_url)

### read in the html from the URL
rosebikes_kinder_html <- rosebikes_kinder_url %>%
  read_html()

#get data from JSON format about the model name and price
rosebikes_kinder_json_tbl <- rosebikes_kinder_html %>%
  html_nodes(css = ".catalog-product-tile__link") %>%
  html_attr("onclick")

#remove "window.dataLayer.push(" and ")"
rosebikes_kinder_tbl <- rosebikes_kinder_json_tbl %>%
  str_remove_all("window.dataLayer.push\\(") %>%
  str_remove("\\)$") %>%
  
  # Convert the JSON format to dataframe
  # map runs that function on each element of the list
  
  map(fromJSON) %>% # need JSON ### need lists
  
  # Extract relevant information of the nested list
  map(purrr::pluck, "ecommerce","click","products") %>% # Need purrr and expl above
  
  # Stack all lists together
  bind_rows() %>%
  # Convert to tibble so that we have the same data format
  as_tibble()
rosebikes_kinder_tbl
```


# My third post
```{r}

#1. Libraries ----
#Lets load some libraries
#Better load a lot of libraries than run into some errors :)
#Dont be surprised when I dont use some

library(glue)
library(httr)
library(purrr)
library(tidyverse) 
library(rvest)     
library(xopen)     
library(jsonlite)  
library(stringi)  
library(jsonlite)
library(readxl)
library(lubridate)
library("writexl")
library(vroom)
library(data.table)
library(tictoc)
library(magrittr)




# Question  Table
# 1 assignee, patent_assignee
# 2 assignee, patent_assignee, patent
# 3 assignee, patent_assignee, uspc

#2.1 Assignee Data ----
assignee_col_types <- list(
  id = col_character(),
  type = col_character(),
  organization = col_character()
)
assignee_tbl <- vroom(
  file       = "~/R_scripts/patent_data/Patent_data_reduced/assignee.tsv", 
  delim      = "\t", 
  col_types  = assignee_col_types,
  na         = c("", "NA", "NULL")
)

#2.2 Patent_assignee Data ----
patent_assignee_col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character()
)
patent_assignee_tbl <- vroom(
  file       = "~/R_scripts/patent_data/Patent_data_reduced/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = patent_assignee_col_types,
  na         = c("", "NA", "NULL")
)

#2.3 Patent Data ----
patent_col_types <- list(
  id = col_character(),
  date = col_date("%Y-%m-%d"),
  num_claims = col_double()
)

patent_tbl <- vroom(
  file       = "~/R_scripts/patent_data/Patent_data_reduced/patent.tsv", 
  delim      = "\t", 
  col_types  = patent_col_types,
  na         = c("", "NA", "NULL")
)
#2.4 USPC data
uspc_col_types <- list(
  patent_id = col_character(),
  mainclass_id = col_character(),
  sequence = col_character()
)

uspc_tbl <- vroom(
  file       = "~/R_scripts/patent_data/Patent_data_reduced/uspc.tsv", 
  delim      = "\t", 
  col_types  = uspc_col_types,
  na         = c("", "NA", "NULL")
)



#3.0 Check for class and Set as data.table
#Check class
class(assignee_tbl)





#SetDT
setDT(assignee_tbl)
setDT(patent_assignee_tbl)
setDT(uspc_tbl)
setDT(patent_tbl)



#Step1: Join data(assignee and patent assignee)
#data.table code

# patent_dominance_tbl <- merge(x = assignee_tbl, y = patent_assignee_tbl, 
#                        by    = c("id" = "assignee_id"), 
#                        all.x = TRUE, 
#                        all.y = FALSE)
# patent_dominance_tbl %>% glimpse()
# 
patent_dominance_tbl <- assignee_tbl %>%
  left_join(patent_assignee_tbl, by = c("id" = "assignee_id"))
patent_dominance_tbl %>% glimpse()



#Step2: Summarize data
patent_dominance_tbl %>%
  group_by(organization) %>%
  summarise(patent_dominance = n()) %>%
  ungroup() %>%
  arrange(desc(patent_dominance))



#CHANGE COLUMN_NAME IN PATENT_TBL, ID=PATENT_ID
setnames(patent_tbl, "id", "patent_id")

recent_patent_activity_tbl <-  patent_dominance_tbl%>%
  left_join(patent_tbl, by = "patent_id")

#Step2: Summarize data by organization and Year
recent_patent_activity_date_tbl <- recent_patent_activity_tbl %>%
  separate(col  = date,
           into = c("year", "month", "day"),
           sep  = "-", remove = FALSE)

recent_patent_activity_date_tbl %>%
  filter(month == 10) %>%
  group_by(organization) %>%
  summarise(recent_patent_activity = n()) %>%
  ungroup() %>%
  arrange(desc(recent_patent_activity))




#Step: Join data(assignee, patent_assignee(patent_dominance_tbl), uspc)
innovation_in_tech_tbl <-  patent_dominance_tbl%>%
  left_join(uspc_tbl, by = "patent_id")

top_10_patents <- innovation_in_tech_tbl %>%
  select(organization, patent_id, mainclass_id) %>%
  group_by(organization,mainclass_id) %>%
  summarise(top_10 = n()) %>%
  ungroup() %>%
  arrange(desc(top_10)) 

top_10_patents %>%
  select(organization,mainclass_id)%>%
  group_by(mainclass_id) %>%
  summarise(top_5_USPO = n()) %>%
  ungroup %>%
  arrange(desc(top_5_USPO))


```

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:

```{r}
samples <- rnorm(100, mean=0, sd=1)
hist(samples)
```

When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.